\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-27 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

These three points indeed deserve careful consideration. We provide separate answers to each of them below.

%\subsubsection{On the justifications for our empirical approach}

\subsubsection{Concern (i): About the assumption of separability}
Our main empirical equation and its underlying assumptions regarding the separability of transport costs between their country- and product-level components draw on the one proposed by \citet{Irrazabal_2015} to estimate the share of additive costs in a firm-level context. It relies on a simple theoretical framework with minimal assumptions, and is compatible with most approaches within the so-called category of ``New Trade Theories''.

Further, we provide a robustness check for this separability assumption that $\tau_{ik} = \tau_i\tau_{k}$ and
 $t_{ik} = t_i +t_k$ in Section 3.3.1 of the paper (Table 2) \textbf{XXX CHECK AT THE END XXX}). We check the robustness of our results by re-running the estimation without the separability assumption. This comes at the cost of a substantial increase in the number of fixed in the regression. In 2019, for example, there are 14,016 country*sector pairs. Adding 28,032 fixed effects (number of country pairs $\times2$ for the two additive and multiplicative costs fixe effects) rather than ``only'' 836 ($(188+230)\times 2$). This is computationally not tractable.
% use "/Users/guillaumedaudin/Documents/Recherche/2013 -- Trade Costs -- local/data/hummels_tra.dta", clear
% keep if year==2019
% keep if mode=="ves"
% gen sector=substr(sitc2,1,3)
% gen blouk = iso_o+sector
% codebook blouk
 For this reason, we have decided to run the robustness check on a reduced sample.
 We select, for each year, the largest importers that form together at least 80\% of annual trade and the largest traded sectors that form together at least 80\% of annual trade.
 We keep in the sample all trade observations from these importers and in these sectors.
 This sample is smaller in terms of observations (2,125 for Air, 5,260 for Vessel on average over the period 1974-2019 (see Table 2), vs more than 30,000 on the complete sample, see Table 1), yet it remains quite large in terms of trade coverage (mean of 68\%).
% use "/Users/guillaumedaudin/Documents/Recherche/2013 -- Trade Costs -- local/results/comparaisons_various/stats_comp_baseline_non_séparé.dta", clear
% gen cover = cover_non_séparé/cover_baseline
% sum cover
\footnote{In the restricted sample, we have around 25 sectors from 14 countries for Air transport, vs 230 sectors from 190 countries in the large sample; and around 50 sectors from 20 countries for Vessel, vs 600 sectors from 190 countries in the complete sample). The vast majority of US imports comes from a selected range of countries, in a selected range of sectors. \textbf{LP: CHECK THE NUMBERS}}
 As we conclude at the end of Section 3.3.1, the trend pattern of the share of additive cost are very similar whether estimated under the separability assumption or not.
 %- see in particular Figures 6 and 7 on pp. 25-26 \textbf{XXX CHECK AT THE END XXX}. Given that the restricted sample covers 80\% of the total trade flows of the US economy, we hope to convince you that this result can be extended to the whole dataset.

\subsubsection{Concern (ii): On the use of non-linear least squares (NLS)} As noted by the referee (and in the paper), it is true that relying on the non-linear least squares method is highly demanding computationally when the number of fixed effects is high. This constraint notably drove us to impose the separability assumption and retain $s=3$ as the relevant sectoral degree of aggregation.

@@

\textit{where $\beta_{ik}$ is the elasticity of transport costs w.r.t. unit price. Given the authors' objective and the data they are using, $\beta$ can be separately estimated for each industry-country pair using the following regression:}

\begin{equation}
\ln f_{ikd} = \beta_{is(k)}\ln \tilde{p}_{ikd} + \text{Controls}_{ikd} +\epsilon_{ikd} \label{eq:estimation_ref1}
\end{equation}

\textit{where $d$ denotes the US district of entry and $k$ denotes an HS10 product} ($f_{ikd}$ being the transport costs). \textit{The
identification of $\beta_{ik}$, in this case, would rely on the across HS10 product and
district-of-entry variation in $f_{ik}$ and $p_{ik}$. Estimating the above equation would
obviously require that the authors do not aggregate up the raw Census data
across all districts and all 10-digit products pertaining to the same 5-digit category. [...] The first advantage of this so-called Hummel's approach is that the above regression can be estimated separately for various country-industry pairs, without imposing Assumptions (a) and (b) outlined above.}

\textbf{Our answer:} First of all, we thank the referee for suggesting to improve the comparison between our method and Hummel's. We took this remark into account by adding a new sub-section in the revised version (Section 2.2, paragraph ``Estimation strategy''). As we now show in this Subsection, the elasticity of transport costs to unit prices $\beta_{ik}$ (in absolute value) also corresponds to the share of additive costs in total transport costs. The share of additive costs can hence be uncovered by regressing transport costs on unit fas prices.

Now coming to the technical side, we thank the referee for his/her relevant suggestion of an alternative estimation method. This drove us to question our own empirical specification deeper. In the end, we decided to maintain our empirical strategy in the revised version, because its advantages seem to overweight the possible costs, and the alternative that the referee suggests does not go without a few important limitations. We develop each line of argument in our answer. Yet, because the referee's estimation method is also an interesting alternative, we added a new section in the Online appendix devoted to it (Section D.3). After reading our answer, we hope to convince you that we made the right choice.

\paragraph{Estimating the share of additive costs: Highlighting some requirements} Our estimated equation relies on non-linear estimation methods, such as Non-Linear Least Squares. However, even with another formulation, such as the one suggested by the referee in Equation (\ref{eq:estimation_ref1}), we would still be constrained to resort to non-linear estimators. This is due to the necessity of imposing an \textit{ex-ante} restriction on parameters, i.e. $\tau \geq 1$ and $t \geq 0$, or $0 \leq  \beta \leq 1$. Should we relax these restrictions, standard linear, least squares estimates often deliver negative, meaningless estimates. In this respect, implementing the referee's method (see below) does not dispose of the requirement of resorting on non-linear estimates (and the computational, time-consuming burden it induces -- though the referee’s method is indeed less computational intensive). Imposing this parameters constraint was not made clear enough in the initial version, and we did our best to make this very important justification clearer in the revised version, as it is now exposed in footnote \textbf{12 page 8}. \textbf{Vérifier à la fin  ? GD}\smallskip

@@

\paragraph{Exploring Referee's alternative functional form \label{subsec:functional_form}}

The estimation strategy suggested by the referee starts from Equation (\ref{eq:Hummels}) linking transport costs and unit prices as assumed in Hummels (2007), yielding Equation (\ref{eq:estimation_ref1}) as estimation equation. By year and transport mode, this implies running the estimation for each country of origin $i$ and each sector $s(k)$ = 3 digit sector, exploiting the variability between sub-sectors at the 10-digit level ($k$) and between ports of entry in the US ($d$). As previously noticed, running this estimation limits the time coverage as information is available at the HS-10 level and by ports of entry only since 2001. We have thus run referee's method over the years 2005-2013, at the $s=3, k=10$ sectoral/product levels, and reported the results in the Online Appendix.

Notice that we are aware of the referee's suggestion to run his/her estimation strategy considering sectoral aggregation at the 5-digit level (with $k=10$). We yet keep considering sectors at the 3-digit aggregation level, in view of being able to compare the pros and cons of the referee's method versus ours, including those years for which the finest disaggregation level is $k=5$ (i.e., the original Hummel's dataset over 1974-1988, as the US Bureau of census import database starts in 1989 --yet being effectively available since 2001 only because of the Covid situation.) \textbf{Est-ec que cet argument peut vraiment être fait puisqu’on fait simplement 2005-2013 ?}

Despite its interest, implementing the referee's method uncovered some drawbacks, that in our view, outweighs those of our method (in particular associated with \textit{Assumptions (a) $\tau_{ik} = \tau_i\tau_{k}$, and (b) $t_{ik} = t_i+ t_{k}$.}) Our answer can be articulated in two steps. First, we challenge the advantages that the referee's estimation method would bring in comparison with ours. Second, we emphasize the drawbacks induced by this method. \smallskip
%
%\paragraph{What we do}
%
%Our estimated equation is written as Equation (\ref{eq:equation0}) with $s$= 3 (or 4) digit and $k$=5 digit (based on Hummel's original dataset from 1974-2004). We thus exploit the variability of transport costs between countries and between 3-digit sectors (conditional on a year and a transport mode, air or vessel). To sum up our methodology:
%\begin{itemize}
%\item Estimating Equation \ref{eq:equation0} provides us with estimates of $\hat{t}_i$, $\hat{t}_{s(k)}$, $\hat{\tau}_i$, $\hat{\tau}_{s(k)}$.
%\item We rebuild
%\begin{eqnarray*}
%\hat{t}_{is(k)} &= &\hat{t}_{i}+\hat{t}_{s(k)} \\
%\hat{\tau}_{is(k)} &= & \hat{\tau}_{i}\times\hat{\tau}_{s(k)}
%\end{eqnarray*}
%\item We deduce the weighted average value of each component $\bar{t}$, $\bar{\tau}$ by year and transport mode, the weighting scheme being the relative value of the flows for each $i,s$ flow, as well as the median, the maximum and the minimum values.
%\item With this in hand, we can (among other things) obtain the estimated share of additive costs in total transport costs for each $i,k$ flow:
%
%
%$$\hat{\beta}_{ik} = \frac{\frac{\hat{t}_{is(k)}}{\tilde{p}_{ik}}}{\tau_{is(k)}-1 + \frac{t_{is(k)}}{\tilde{p}_{is(k)}}} $$
%\end{itemize}
%
%\paragraph{What the referee suggests to do}
%
%The estimation strategy suggested by the referee starts from Equation (\ref{eq:Hummels}) linking transport costs and unit prices as assumed in Hummels (2007). As shown in Subsection (\ref{ssec:interpret_beta}), the elasticity of transport costs to unit prices $\beta_{ik}$ (in absolute value) also corresponds to the share of additive costs in total transport costs. The share of additive costs can hence be uncovered by regressing transport costs on unit (ie, fas) prices. Specifically, the referee suggests to run the estimation based on Equation (\ref{eq:estimation_ref1}).
%
%Precisely, by year and transport mode, this implies running the estimation for each country of origin $i$ and each sector $s(k)$ = 3 digit sector, exploiting the variability between sub-sectors at the 10 digit level ($k$) and between ports of entry in the US ($d$).\footnote{The referee suggests to run his/her proposed estimation strategy considering sectoral aggregation at the 5-digit level (with $k=10$). We followed his suggestion but considering the 3-digit level. We made this choice in view of being able to compare the pros and cons of the referee's method versus ours. In Hummels' (2007) database, which we use until 2004, the finest degree of classification is at the 5-degree level until 2004. For comparability reasons over time, we adopt the same degree of classification $k=5$ for the following years (based on the original Census dataset). As a result, transport costs are estimated at the 3-digit level as benchmark estimate, exploiting heterogeneity at the 5-digit level (for a given origin country, and conditional on year and transport mode). This has driven us to retain $s=3$ when implementing the referee's method, in view of preserving comparability between both strategies.}

@@

\paragraph{a) The advantages of the referee's method are not as important as suggested}

\begin{itemize}
\item \textit{The first advantage of this so-called Hummel's Approach is that the above
regression can be estimated separately for various country-industry pairs, without
imposing Assumptions (a) $\tau_{ik} = \tau_i\tau_{k}$, and (b) $t_{ik} = t_i+ t_{k}$.} \\

\textbf{Our answer:}

First, as already discussed in our letter, the separability assumption does not seem to be a strong assumption. This is based on the conclusion drawn from the robustness check on a reduced sample. If it is smaller in terms of observations, it yet remains quite large in terms of trade coverage, as the selected countries and sectors (at the 3-digit level) constitute 68\% of the total value of flows (on a yearly basis). As we conclude at the end of Section 3.3.1, whatever the transport mode and for both types of transport costs, the trend patterns of international transport costs are very similar whether estimated under the separability assumption or not.

### 2021-10-27 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex

For both transport modes the distribution of $\beta_{ikt}$ over the triplet (year, country of origin, product) appears smoothly distributed over the interval $[0,1]$, whatever the assumption regarding the specification of fixed effects.
Relaxing the assumption that fixed effects are separable between the two country and product dimensions does not alter qualitatively our conclusion, that the elasticity of transport costs to the export price (or the share of additive costs in total transport costs), is strongly varying over time, countries of origin and products.
\footnote{As a consequence, this also provides an indirect robustness check to the results regarding the trend decomposition provided in Section 4 of the paper, which establish that the decline of ``pure'' transport costs is a main reason for the decrease of overall transport costs observed over time.}

>>>>

\textbf{Je ne comprends pas ce paragraphe. La footnote semble être ancienne. Mais en quoi est-ce que les histogrammes nous aident ? Éventuellement à dire qu’il y a moins de solutions de coin lorsqu’on fait l’estimation en séparé ? G.D.}For both transport modes the distribution of $\beta_{ikt}$ over the triplet (year, country of origin, product) appears smoothly distributed over the interval $[0,1]$, whatever the assumption regarding the specification of fixed effects.
Relaxing the assumption that fixed effects are separable between the two country and product dimensions does not alter qualitatively our conclusion, that the elasticity of transport costs to the export price (or the share of additive costs in total transport costs), is strongly varying over time, countries of origin and products.
\footnote{As a consequence, this also provides an indirect robustness check to the results regarding the trend decomposition provided in Section 4 of the paper, which establish that the decline of ``pure'' transport costs is a main reason for the decrease of overall transport costs observed over time.}
